Interactive Visual Analytics of Image-Centric Cohort Study Data

### 2014-03-04 draft.tex
improved Structure

%% indicate IEEE Member or Student Member in form indicated below
\author{Paul Klemm}
\authorfooter{
%% insert punctuation at end of each item
\item
 Otto-v.-Guericke-University Magdeburg
}

@@

My Text

\section{Medical and Technical Background}

\section{Prior and Related Work}

@@

>>>>

%% indicate IEEE Member or Student Member in form indicated below
\author{TBA}
\authorfooter{
%% insert punctuation at end of each item
\item
 Otto-v.-Guericke-University Magdeburg
}

@@

\section{Medical and Technical Background}
\textbf{Image aquisition}\\
- standardization of MR Scanners

\subsection{Epidemiological Workflow}
Bernhards Paper

\subsection{The Spine Dataset}

\section{Prior and Related Work}
- VMV Paper\\
- Analysis of data in the Rotterdam study\\
- VA in Epidemiology Part of Bernhards Paper
	- Commercial visual Analytics Systems

@@

According to Steffens Terminology in Interactive Visual Analysis of Perfusion Data
\\\\
\textbf{Object Space}\\
- Medical Image Data / Spine Segmentations\\
\textbf{Attribute Space}\\
- SHIP-Variables\\
- Derived visualizations

? Where to incorporate Levels of IVA

\subsection{Feature Localization}
- Projection from Image Space to Attribute data. This is more difficult in our application, because we currently only brush on derived features.\\
- Clustering in Image Space yields Groups which can be analyzed using the attribute space

\subsection{Local Investigation}
- Selection of Information using Bar Charts, Scatterplots or Parallel Coordinates which projects the selection into the Object space\\
- this selection is for categorical data already given implicitly bei projecting the 3D-View onto the Bar Charts/Mosaik Plots!\\
- this aims to locale features of the data!\\
- Gain Information about SHIP-Variables by putting them into the context of each other. The Pivot Table allows for direct numerical\\ analysis, while the information visualizations allow for better insight of the combination

\subsection{Multivariate Analysis}
- Selection of Elements in Scatterplots, Barcharts or Parallel Coordinates Views - observe how selection changes another view - this allows for multivariate analysis\\
- Becker, R.A., Cleveland, W.S.: Brushing scatterplots. Technometrics 29(2) (1987)\\
- Wang Baldonado, M.Q., Woodruff, A., Kuchinsky, A.: Guidelines for using multiple views in information visualization. In: AVI ’00: Proceedings of the working conference on Ad- vanced visual interfaces, pp. 110–119. ACM Press, New York, NY, USA (2000). DOI\\ http://doi.acm.org/10.1145/345513.345271
- By brushing individual parameters or create new binnings of parameter it is possible to see how they change in coordinated views. This is already implemented in the Cargo framework\\
- by creating comparative 3d Visualizations it is possible to assess the influence of non-image parameters to the visual space.
